Weather covariance matrices as U_hyp for GR50

### 2021-02-04 R/Analysis_v0.6_weather_covariance_Uhyp_greenup.Rmd
Finish manuscript v0.6 Intro-Discussion and four Figures
Completed manuscript v0.8 and edited figures for consistency

cov_gg$ggobject + 
  ggtitle("Gulf greenup", subtitle = "8.4% SNP mass")
cov_gf$ggobject + 
  ggtitle("Gulf flowering", subtitle = "31.8% SNP mass")
cov_mg$ggobject + 
  ggtitle("Midwest greenup", subtitle = "28.6% SNP mass")
cov_mf$ggobject + 
  ggtitle("Midwest flowering", subtitle = "45.1% SNP mass")
cov_gamg$ggobject + 
  ggtitle("Gulf and Midwest greenup", subtitle = "8.5% SNP mass")
cov_gamf$ggobject + 
  ggtitle("Gulf and Midwest flowering", subtitle = "47.3% SNP mass")
```
47.3% of effect mass for both subpop flowering was on hyp matrices, while only 8.5% of greenup was.
Gulf greenup: 8.4%  flowering: 31.8%
Midwest greenup: 28.6% flowering 45.1%

@@

cov_flex$phe <- factor(cov_flex$phe, levels = c("tave_18d", "tave_10d", "dyln_fl50", "cgdd_12c_gr2fl"))

@@

@@

save_plot(filename = "Figure_2_Covariance_matrices_and_posterior_weights.png", plot = last_plot(), base_height = 8, base_width = 9)
```

>>>>

cov_gg$ggobject + 
  ggtitle("Gulf greenup", subtitle = "8.4% SNP mass")
cov_gf$ggobject + 
  ggtitle("Gulf flowering", subtitle = "31.8% SNP mass")
cov_mg$ggobject + 
  ggtitle("Midwest greenup", subtitle = "28.6% SNP mass")
cov_mf$ggobject + 
  ggtitle("Midwest flowering", subtitle = "45.1% SNP mass")
cov_gamg$ggobject + 
  ggtitle("Gulf and Midwest greenup", subtitle = "8.5% SNP mass")
cov_gamf$ggobject + 
  ggtitle("Gulf and Midwest flowering", subtitle = "47.3% SNP mass")
```
47.3% of effect mass for both subpop flowering was on hyp matrices, while only 8.5% of greenup was.
Gulf greenup: 8.4%  flowering: 31.8%
Midwest greenup: 28.6% flowering 45.1%
```{r}
5.127744e-02/4.037520e-01
```

@@

cov_flex$phe <- factor(cov_flex$phe, levels = c("tave_18d", "tave_10d", "dyln_fl50", "cgdd_12c_gr2fl"))
cov_flex$subpop <- factor(cov_flex$subpop, levels = c("Gulf", "Midwest", "Both)"))

@@

df_2gr_b$subpop <- factor(df_2gr_b$subpop, levels = c("Gulf", "Midwest", "Both"))
df_2fl_b$subpop <- factor(df_2fl_b$subpop, levels = c("Gulf", "Midwest", "Both"))
df_2gr_a$subpop <- factor(df_2gr_a$subpop, levels = c("Gulf", "Midwest", "Both"))
df_2fl_a$subpop <- factor(df_2fl_a$subpop, levels = c("Gulf", "Midwest", "Both"))

@@

save_plot(filename = "../manuscript/plots/Figure_2_Covariance_matrices_and_posterior_weights.svg", plot = last_plot(), base_height = 8, base_width = 9)
```
